Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-01 paper/v1.0/sections/3_floquet_theory.tex
Corrections

First we need to identify the \textit{quasienergies} and periodic \textit{Floquet modes} for derived wavefunctions in Eq.~(\ref{eq_2}). By factorizing the wavefunction into a linearly time dependent part and a peridic time dependend part, the quasienergies can be present as
\begin{equation} \label{eq_6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
which is only depend on single quantum number ($n$) and Floquet modes are given by
\begin{equation} \label{eq_7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) = &
    \frac{1}{\sqrt{L_x}} \chi_{n}\left[y - y_0 - \zeta(t)\right]
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x \\
     & +
     \frac{eE(y - y_0)}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg),
  \end{aligned}
\end{equation}
with
\begin{equation} \label{eq_8}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)} ~ \text{and} ~
  \xi = \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
\end{equation}
It is important to notice that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions.
Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in position space as
\begin{equation} \label{eq_9}
  \psi_{n,m}(x,y,t) =
  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (x,y,t).
\end{equation}
Then performing Fourier trasform over the confined two-dimentional space $A=L_xL_y$, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
\begin{equation} \label{eq_10}
  \begin{aligned}
    \phi_{n,m}(k_x,k_y,t)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + y_0]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_11}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{n} \qty(\frac{k}{\kappa})
\end{equation}
and
\begin{equation} \label{eq_12}
  b \equiv
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad
  d \equiv
 \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
\end{equation}
For details of the formalism the authors refer to Appendix B.

>>>>

First we need to identify the \textit{quasienergies} and periodic \textit{Floquet modes} for derived wavefunctions in Eq.~(\ref{eq_2}). By factorizing the wavefunction into a linearly time dependent part and a peridic time dependend part, the quasienergies can be present as
\begin{equation} \label{eq_6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
which is only depend on single quantum number ($n$) and Floquet modes are given by
\begin{equation} \label{eq_7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) = &
    \frac{1}{\sqrt{L_x}} \chi_{n}\left[y - y_0 - \zeta(t)\right]
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x \\
     & +
     \frac{eE(y - y_0)}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg),
  \end{aligned}
\end{equation}
with
\begin{equation} \label{eq_8}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)} ~ \text{and} ~
  \xi = \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
\end{equation}
It is important to notice that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions.

Then performing Fourier trasform over the confined two-dimentional space $A=L_xL_y$, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
\begin{equation} \label{eq_10}
  \begin{aligned}
    \phi_{n,m}(k_x,k_y,t)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + y_0]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_11}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{n} \qty(\frac{k}{\kappa})
\end{equation}
and
\begin{equation} \label{eq_12}
  b \equiv
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad
  d \equiv
 \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
\end{equation}
For details of the formalism the authors refer to Appendix B. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
\begin{equation} \label{eq_9}
  \psi_{n,m}(k_x,k_y,t) =
  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (k_x,k_y,t).
\end{equation}

### 2021-07-01 paper/v1.0/sections/appendix_b.tex
Corrections

To write the Floquet modes in momentum space, we perform continuous Fourier transform over the considering confined space $A=L_xL_y$ for Eq.~(\ref{eq_7})
\begin{equation} \label{eq_b8}
  \begin{aligned}
    \phi_{n,m}(k_x,k_y,t)  &=
    \int_{-L_y/2}^{L_y/2} dy\; \exp(-i\qty[k_y - \gamma(t)]y)
    \chi_{n}\qty[y - \mu(t)] \\
     & \times
     \frac{1}{\sqrt{L_x}}
     \int_{-L_x/2}^{L_x/2} dx\;
     \exp(-ik_x x)
     \exp( \frac{i p_x }{\hbar}x ) \\
     &
     \times
     \exp(
      \frac{-i\gamma(t)}{\hbar}
      y_0)
     \exp(\frac{-i}{\hbar}
     \qty[
     m_e \dot{\zeta}(t) \zeta(t) - \xi
     ]),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_b9}
  \mu(t) \equiv \frac{eE\sin(\omega t)}{m_e(\omega_0^2 - \omega^2)} + y_0
  \quad,\quad
  \gamma(t) \equiv
  \frac{eE\omega_0^2\cos(\omega t)}{\hbar\omega(\omega_0^2 - \omega^2)}.
\end{equation}
Next using the identity \cite{bruus04}
\begin{equation} \label{eq_b10}
  \int_{L_x} dx\;
  \exp( -ik_x x + \frac{i p_x }{\hbar}x ) =
  L_x \delta_{k_x,\frac{p_x}{\hbar}},
\end{equation}
we can derive
\begin{equation} \label{eq_b11}
  \begin{aligned}
    \phi_{n,m}(k_x,k_y,t)  =
    \exp(
     \frac{-i\gamma(t)}{\hbar}
     y_0) &
    \exp(\frac{-i}{\hbar}
    \qty[
    m_e \dot{\zeta}(t) \zeta(t) - \xi
    ]) \\
    & \times
    \Phi_{n,m}(k_y,t)
    \delta_{k_x,\frac{p_x}{\hbar}}.
  \end{aligned}
\end{equation}
Here we defined $\Phi_{n,m}(k_y,t)$ as
\begin{equation} \label{eq_b12}
  \Phi_{n,m}(k_y,t) \equiv
  \sqrt{L_x}
  \int_{-L_y/2}^{L_y/2} dy\;
  \chi_{n}\qty[y - \mu(t)]
  \exp(
    -i\qty[k_y - \gamma(t)]
    y).
\end{equation}
Subtituting $  {k'_y} = k_y -\gamma(t)$ and $y' = y -\mu(t)$ and assuming that size of the 2DEG sample in $y$-direction is large ($L_y \rightarrow \infty$), we can obtain
\begin{equation} \label{eq_b13}
  \Phi_{n,m}({k'_y} ,t) =
  {\sqrt{L_x}} e^{-i {k'_y}\mu}
  \int_{-\infty}^{\infty} dy'\;
  \chi_{n}\qty(y')
  \exp(-i{k'_y} y').
\end{equation}
We can identify that the integral represnts the Fourier transform of $\{\chi_n\}$ functions and using the symmetric conditions \cite{bruus04} for the Fourier transform of Gauss-Hermite functions $\vartheta_n(x)$:
\begin{equation} \label{eq_b14}
  \mathcal{FT}[\vartheta_n(\kappa x),x,k] = \frac{i^n}{|\kappa|}\vartheta_n(k/\kappa),
\end{equation}
Eq.~(\ref{eq_b13}) can be simplified as
\begin{equation} \label{eq_b15}
  \Phi_{n,m}({k'_y} ,t) =
    \sqrt{L_x}e^{-i {k'_y}\mu}
    \tilde{\chi}_{n}\qty({k'_y}),
\end{equation}
with
\begin{equation} \label{eq_b16}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{\alpha} \qty(\frac{k}{\kappa}).
\end{equation}
Subtitute Eq.~(\ref{eq_b15}) back in Eq.~(\ref{eq_b11}) and this leads to
\begin{equation} \label{eq_b17}
  \begin{aligned}
    \phi_{n,m}(k_x,k_y,t)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + \frac{\hbar k_x}{eB}]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_b18}
  b \equiv
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad
  d \equiv
 \frac{eE}{m_e(\omega_0^2 - \omega^2)},
\end{equation}
and it is necessary to notice that $k_x$ is quantized with $k_x = 2\pi m/L_x ~,~ m \in \mathbb{Z}$.

>>>>

To write the Floquet modes in momentum space, we perform continuous Fourier transform over the considering confined space $A=L_xL_y$ for Eq.~(\ref{eq_7})
\begin{equation} \label{eq_b8}
  \begin{aligned}
    \phi_{n,m}(k_x,k_y,t)  &=
    \int_{-L_y/2}^{L_y/2} dy\; \exp(-i\qty[k_y - \gamma(t)]y)
    \chi_{n}\qty[y - \mu(t)] \\
     & \times
     \frac{1}{\sqrt{L_x}}
     \int_{-L_x/2}^{L_x/2} dx\;
     \exp(-ik_x x)
     \exp( \frac{i p_x }{\hbar}x ) \\
     &
     \times
     \exp(
      \frac{-i\gamma(t)}{\hbar}
      y_0)
     \exp(\frac{-i}{\hbar}
     \qty[
     m_e \dot{\zeta}(t) \zeta(t) - \xi
     ]),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_b9}
  \mu(t) \equiv \frac{eE\sin(\omega t)}{m_e(\omega_0^2 - \omega^2)} + y_0
  \quad,\quad
  \gamma(t) \equiv
  \frac{eE\omega_0^2\cos(\omega t)}{\hbar\omega(\omega_0^2 - \omega^2)}.
\end{equation}
Next using the identity \cite{bruus04}
\begin{equation} \label{eq_b10}
  \int_{L_x} dx\;
  \exp( -ik_x x + \frac{i p_x }{\hbar}x ) =
  L_x \delta_{k_x,\frac{p_x}{\hbar}},
\end{equation}
we can derive
\begin{equation} \label{eq_b11}
  \begin{aligned}
    \phi_{n,m}(k_x,k_y,t)  =
    \exp(
     \frac{-i\gamma(t)}{\hbar}
     y_0) &
    \exp(\frac{-i}{\hbar}
    \qty[
    m_e \dot{\zeta}(t) \zeta(t) - \xi
    ]) \\
    & \times
    \Phi_{n,m}(k_y,t)
    \delta_{k_x,\frac{p_x}{\hbar}}.
  \end{aligned}
\end{equation}
Here we defined $\Phi_{n,m}(k_y,t)$ as
\begin{equation} \label{eq_b12}
  \Phi_{n,m}(k_y,t) \equiv
  \sqrt{L_x}
  \int_{-L_y/2}^{L_y/2} dy\;
  \chi_{n}\qty[y - \mu(t)]
  \exp(
    -i\qty[k_y - \gamma(t)]
    y).
\end{equation}
Subtituting $  {k'_y} = k_y -\gamma(t)$ and $y' = y -\mu(t)$ and assuming that size of the 2DEG sample in $y$-direction is large ($L_y \rightarrow \infty$), we can obtain
\begin{equation} \label{eq_b13}
  \Phi_{n,m}({k'_y} ,t) =
  {\sqrt{L_x}} e^{-i {k'_y}\mu}
  \int_{-\infty}^{\infty} dy'\;
  \chi_{n}\qty(y')
  \exp(-i{k'_y} y').
\end{equation}
We can identify that the integral represnts the Fourier transform of $\{\chi_n\}$ functions and using the symmetric conditions \cite{celeghini21} for the Fourier transform of Gauss-Hermite functions $\theta_n(x)$:
\begin{equation} \label{eq_b14}
  \mathcal{FT}[\theta_n(\kappa x),x,k] = \frac{i^n}{|\kappa|}\theta_n(k/\kappa),
\end{equation}
Eq.~(\ref{eq_b13}) can be simplified as
\begin{equation} \label{eq_b15}
  \Phi_{n,m}({k'_y} ,t) =
    \sqrt{L_x}e^{-i {k'_y}\mu}
    \tilde{\chi}_{n}\qty({k'_y}),
\end{equation}
with
\begin{equation} \label{eq_b16}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{\alpha} \qty(\frac{k}{\kappa}).
\end{equation}
Subtitute Eq.~(\ref{eq_b15}) back in Eq.~(\ref{eq_b11}) and this leads to
\begin{equation} \label{eq_b17}
  \begin{aligned}
    \phi_{n,m}(k_x,k_y,t)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + \frac{\hbar k_x}{eB}]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_b18}
  b \equiv
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad
  d \equiv
 \frac{eE}{m_e(\omega_0^2 - \omega^2)},
\end{equation}
and it is necessary to notice that $k_x$ is quantized with $k_x = 2\pi m/L_x ~,~ m \in \mathbb{Z}$.
